NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-03-06 Manuscript/manuscriptPS.tex
Added MacRog POPS data to Fig 5.

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers without additional ions}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for the computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
  \todo{CHARMM36-UA point for alpha in wrong place?} \\
  \todo{MacRog POPS data should be added.} \\
  \todo{In table \ref{IONsystems}: ''CKP1 referes to the version with  
    Berger/chiu NH3 charges compatible with Berger
    and CKP2 to the version with more Gromos compatible version.'' Is this correct
    also in this figure?} \\
  \todo{Lipid17 results should be added.} \\
  \todo{We should also add CHARMM36 POPS ran with K counterions: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/1\#issuecomment-308570874}
\end{figure}

>>>>

\subsection{Headgroup and glycerol backbone in simulations of PS lipid bilayers without additional ions}
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPS.pdf}
  \caption{\label{HGorderParametersPS}
    Order parameters for PS headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    Experimental data from \cite{browning80} contains 0.1M of NaCl.
    Signs are taken from experiments for POPS described in Supplementary Information.
    The vertical bars shown for most computational values are not error bars, but demonstrate that for these systems we had at least two data sets; the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average.
  }
  \todo{In table \ref{IONsystems}: ''CKP1 referes to the version with  
    Berger/chiu NH3 charges compatible with Berger
    and CKP2 to the version with more Gromos compatible version.'' Is this correct
    also in this figure?} \\
  \todo{Lipid17 results should be added.} \\
  \todo{We should also add CHARMM36 POPS ran with K counterions: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/1\#issuecomment-308570874}
\end{figure}
